---
title: "p8105_hw5_kmw2189"
author: "Kylie Wheelock Riley"
date: "11/11/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

## Problem 1

Uses the iris dataset from the tidyverse package and there are some missing values in each column. The purpose of this problem is to fill in those missing values.

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

1) For numeric variables, you should fill in missing values with the mean of non-missing values
2) For character variables, you should fill in missing values with "virginica"

Instructions:
and returns the resulting vector. 
Apply this function to the columns of iris_with_missing using a map statement
```{r}
## code outside of the function that replaces numeric with mean of other values 
iris_with_missing %>% 
  mutate(
    sepal_length = replace_na(sepal_length, mean(sepal_length, na.rm = TRUE)),
    sepal_length = round(sepal_length, digits = 2),
    species = replace_na(species, "virginica")
  )

```

```{r}

## write a function that takes a vector as an argument. 

replace_iris = function(column_name) {
  
  ##replaces missing values using the rules defined above;
  if(is.numeric(column_name))
    {
    new_val = replace_na(column_name, mean(column_name, na.rm = TRUE))
  } 
  
  else if(is.character(column_name))
  {
    new_val = replace_na(column_name, "virginica")
  }
  
}
  replace_iris(iris_with_missing)

```

