---
title: "p8105_hw5_kmw2189"
author: "Kylie Wheelock Riley"
date: "11/11/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

## Problem 1

Uses the iris dataset from the tidyverse package and there are some missing values in each column. The purpose of this problem is to fill in those missing values.

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

1) For numeric variables, you should fill in missing values with the mean of non-missing values
2) For character variables, you should fill in missing values with "virginica"

Instructions:
Write a function that takes a vector as an argument; 
replaces missing values using the rules defined above; 
and returns the resulting vector. 
Apply this function to the columns of iris_with_missing using a map statement
```{r}
## want to write code outside of a function to do what we want. 
iris_with_missing %>% 
  mutate(
    sepal_length = replace_na(sepal_length, mean(sepal_length, na.rm = TRUE))
  )

  

##iris_with_missing$sepal_length[which(is.na(iris_with_missing$sepal_length))] = mean(iris_with_missing$sepal_length, na.rm = TRUE)
```

```{r}

## write a function that takes a vector as an argument. 
replace_iris = function(column_name) {
  
 column_numeric = read.csv(file = filename) %>% 
     gather(key = week, value = value)
 column_character = 
  
##}

##z_scores(x_vec)
```

