---
title: "p8105_hw5_kmw2189"
author: "Kylie Wheelock Riley"
date: "11/11/2019"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))

```

## Problem 1

Uses the iris dataset from the tidyverse package and there are some missing values in each column. The purpose of this problem is to fill in those missing values.

1) For numeric variables, you should fill in missing values with the mean of non-missing values
2) For character variables, you should fill in missing values with "virginica"

```{r loading problem 1 data}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) %>% 
  janitor::clean_names()
```

```{r problem 1 trial code, include = FALSE}
## code outside of the function that replaces numeric with mean of other values 
iris_with_missing %>% 
  mutate(
    sepal_length = replace_na(sepal_length, mean(sepal_length, na.rm = TRUE)),
    sepal_length = round(sepal_length, digits = 2),
    species = replace_na(species, "virginica")
  )

```

```{r problem 1 function and map}
## write a function that takes a vector as an argument. 
replace_iris = function(col_name){
  

  if(is.numeric(col_name))
    {
    new_value = replace_na(col_name, mean(col_name, na.rm = TRUE))
  } 
  
  else if(is.character(col_name))
    {
    new_value = replace_na(col_name, "virginica")
  }
  
  new_value
}

iris_without_missing = map_dfr(iris_with_missing, replace_iris)
```


## Problem 2
Problem 2 contains data from a longitudinal study that included a control arm and an experimental arm. Data for each participant is included in a separate file, and file names include the subject ID and arm.

Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:

```{r loading problem 2 data}
##Start with a dataframe containing all file names; the list.files function will help
files = list.files(path = "./data", pattern = "*.csv", full.names = TRUE) %>% 
  set_names()

```


Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.


start with a tibble, this tibble contains file and path
use mutate to pull data.
##convert to vector = as.vector
##str-c
##create a lable by yourself
##pivot longer the week
##group cols
##map read.csv


